A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-15 paper.tex
Cite IPFS

The structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload. This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point. Figure.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint. Furthermore, MAM attaches messages chronologically, which preserves the correct order of IoT streaming data. Though combining other distributed storage like IPFS with signature schemes can also preserve the order of each record, the problem surfaced if the order maintained is wrong.

>>>>

The structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload. This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point. Figure.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint. Furthermore, MAM attaches messages chronologically, which preserves the correct order of IoT streaming data. Though combining other distributed storage like IPFS\cite{IPFS} with signature schemes can also preserve the order of each record, the problem surfaced if the order maintained is wrong.
